Problem Set 4 (Answers)

### 2019-11-24 static/homeworks/04-problem-set-answers.Rmd
Update format for HW 4 answers

---
title: "Problem Set 4 (Answers)"
author: "Ryan Safner" # put your name here! 
date: "ECON 480 - Fall 2019"
output: html_document # change to pdf if you'd like, this will make a webpage (you can email it and open in any browser)
---

>>>>

---
title: "Problem Set 4 (Answers)"
author: "Ryan Safner"
date: "ECON 480 - Fall 2019"
output:
  html_document:
    df_print: paged
    #theme: simplex
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango
---
